Audiovisual Analytics of social linked data

### 2017-11-13 latex/nuvem/nuvem2.tex
finalizada primeira revisao

\subsection{Perceptual framework}
Frequency and intensity are related to pitch and volume
through the Weber-Fechner laws.
One might also think about durations on the same sense.
Visual estimuli, on the other hand, seem to be 
more often modeled as the Steven's law.
Is it possible to relate frequency and intensity to
pitch and loudness through Steven's laws?
Is the perception of visual cues also fit by the Weber-Fechner?
The Steven's law is a power law while Weber-Fechner is an exponential
law.
This entails:
\begin{equation}
	\Delta p = log_X(e_1/e_0)
\end{equation}
\noindent for Weber-Fechner and
\begin{equation}
	p = k.e_1^\alpha
\end{equation}
\noindent for Steven's,
where p is the (subjective) magnitude of the perceived stimuli,
$X$ and $\alpha$ depend on the stimuli,
and $e_0$ and $k$ depend on the the units used.

In equally spaced samples of the stimuli (e.g. in PCM audio),
the sample values might express amplitude or frequency.
If the sample values represent durations, the separation
between samples looses its meaning, but enables a Fourier
analysis in a 'virtual' or 'imaginary' space.

The possible equations relating physical and perceived stimuli
should be integrated to AAVO.

========

	Some perception measurements are very consistently represented by
	exponentil laws, such as betweeen pich and frequency.
	Loudness is also more or less consistently related by exponentials
	to the power, intensity or amplitude for a fixed frequency or spectrum.
	Visual cues, on the other hand, present consistent power laws.

	mention the human processor model.

	Related to sound, most traditional notation and musical qualities
	respect the Weber-Fechner law, with note grids (e.g. semitones, octaves),
	respecting the logarithm of frequency: interval$=log_2(f_1/f_0)$,
	loudness$=log_10(p_1/p_0)$.
	Duration seems also to be conceptualized as such
	because musical notation uses the division in two (simple, imperfectus),
	amd three (perfectus) yielding a grid having
	$d_i=d_{i+1}/2$ and $d_i=d_{i+1}/3$.
	$durations=2^{x-i}$ and $=3^{x-i}$.
	Which implies $log_2(dur) = x-i$.
	A Weber-Fechner compliant relation
	between the number of the durations and
	depth of the division x-i = (4, 8, 16) for simple,
	(3, 9, 12) for compound,
	(5,7,13) complex.
	6 is compound in traditional music theory,
	but is the only one that relates periods of 2 and 3,
	subdivision of 2 and 3.

\subsection{Other: Erdös Sectioning, KS-derived statistics, Wordnet,
text mining, stability and differentiation, partnerships}
Other works, such as classification of participants (vertices) as
hubs, intermediary and periphery, statistical tests e.g. to
observe linguistic differences among the network participants,
the use of Wordnet and token-oriented methods for text mining,
and current partnership with researchers in physics, computer science,
mathematics, philosopy and social sciences, clinical and social psychology,
give some of the support for our endeavors.

\subsection{What to do?}
We will surely integrate the Hypothesis, Goals, Interaction
concepts into the AAVO Core.
We should develop the system in Section~\ref{sys} to some extent,
maybe for concept proofs or simple prototyping.

With the research groups @Nuvem, 
relate the missing concepts in AAVO,
enhance the software design of the system,
Know about the right tools for visualizing
ontologies and social data.
For knowing about pertinent analysis methods
and known conceptualizations.
Virtual reality, visualization and societal groups
might want to formalize their own conceptualizations,
and concepts related to AAVO might have similar developments
or which are confluent (e.g. symbiotic)
with Section~\ref{current}: software
theoretical framework, research and institutional experiments and equipment,
linked data, and other initiatives or knowledge.

@@

>>>>

\subsection{Perceptual framework}
Frequency and intensity are related to pitch and volume
through the Weber-Fechner law.
One might also think about durations on the same sense.
Visual estimuli, on the other hand, seem to be 
more often modeled as the Steven's law (is this true?).
Is it possible to relate frequency and intensity to
pitch and loudness through Steven's law?
Is the perception of visual cues also fit by Weber-Fechner?
The Steven's law is a power law while Weber-Fechner is an exponential
law:
\begin{equation}
	\Delta p = log_X(e_1/e_0)
\end{equation}
\noindent for Weber-Fechner and
\begin{equation}
	p = k.e_1^\alpha
\end{equation}
\noindent for Steven's,
where p is the (subjective) magnitude of the perceived stimuli,
$X$ and $\alpha$ depend on the stimuli,
and $e_0$ and $k$ depend on the the units used.
$\Delta p$ is an interval, a distance, in the perceived magnitude.

In equally spaced samples of the stimuli (e.g. in PCM audio),
the sample values might express amplitude or frequency.
If the sample values represent durations, the separation
between samples looses its meaning, but enables a Fourier
analysis in a 'virtual' or 'imaginary' space.
For example, consider the Fouriter transform of
this sequence of durations in seconds:
[1, 0.5, 0,5, 1, 0.5, 0.5].
The components are sinusoids whose amplitude
is duration.
The durations are the sample values,
each value corresponding to a sample separated
by a virtual distance.
% keep static amplitude or phase
% in virtual and real-simed Fourier transfoms

Related to sound, most traditional music notation and qualities
respect the Weber-Fechner law, with note grids (e.g. semitones, octaves),
respecting the logarithm of frequency: interval$=log_2(f_1/f_0)$,
loudness$=log_10(p_1/p_0)$.
Duration seems also to be conceptualized as such
because musical notation uses the division in two (simple, imperfectus),
amd three (perfectus) yielding a grid having
$d_i=d_{i+1}/2$ and $d_i=d_{i+1}/3$.
$durations=2^{x-i}$ and $=3^{x-i}$.
Which implies $log_2(dur) = x-i \Rightarrow i = log_2(X/dur), x = log_2X$.
A Weber-Fechner compliant relation
between the number of the durations and
depth of the division x-i = (4, 8, 16) for simple,
(3, 9, 12) for compound,
(5,7,13) complex.
6 is compound in traditional music theory,
but is the only one that relates periods of 2 and 3,

The Human Processor Model~\cite{HPM}
has somewhat established values for
a number of cognitive characteristics such as eye movement time (230ms),
half-life of visual image storage (200ms) and 
of
working memory (7s),
and visual and auditory capacities (17 letters, 5 letters).
These reference values, together with the
equations relating physical and perceived stimuli,
should be integrated to AAVO.

\subsection{Other: Erdös Sectioning, KS-derived statistics, Wordnet,
text mining, stability and differentiation, partnerships}
Other works, such as the classification of participants (vertices) as
hubs, intermediary and peripheral; statistical tests e.g. to
observe linguistic differences among the network participants;
the use of Wordnet and token-oriented methods for text mining;
and current partnership with researchers in physics, computer science,
mathematics, philosopy and social sciences, clinical and social psychology,
give some of the support for our endeavors.

\subsection{What to do?}
We will surely integrate the envisioned concepts into AAVO Core.
We should develop the system in Section~\ref{sys} to some extent,
maybe for concept proofs or simple prototyping.

With the research groups @Nuvem, 
especially those audiovisual and societal,
relate the missing concepts in AAVO,
enhance the software design of the system.
Know about the right tools for visualizing
ontologies and social data.
For knowing about pertinent analysis methods
and known conceptualizations.
might want to formalize their own conceptualizations,
and concepts related to AAVO might have similar developments
or which are confluent (e.g. symbiotic)
with Section~\ref{current}: software,
theoretical framework, research and institutional experiments and equipment,
linked data, and other initiatives or knowledge.

@@

\bibitem{HPM}
	Human processor model. (2017, March 11). In Wikipedia, The Free Encyclopedia. Retrieved 06:16, November 13, 2017, from \url{https://en.wikipedia.org/w/index.php?title=Human_processor_model&oldid=769706845}
